---
title: "CEN Cluster Analysis_RT residuals of tasks"
author: "Echo Mei Xu"
date: '2024-04-22'
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(dplyr)
library(writexl)
library(ggplot2)
library(tidyverse)
library(knitr)
library(lme4)
library(purrr)
library(cluster)
library(reshape2)
library(tibble)

cen.stroop <- read_excel ("/Users/echo/Library/CloudStorage/OneDrive-UNSW/Brain_Stimulation/CEN_Study_One/Data_Analysis/results/cog/20230814_cen_cog.xlsx", sheet = "stroop")
cen.stroop$session <- factor (cen.stroop$session, levels = c('S1', 'S2', 'S3'))
cen.stroop$session <- as.numeric(cen.stroop$session)
cen.stroop <- cen.stroop %>%
  mutate(participant = as.factor(participant), task_order = as.factor(task_order), order = as.factor(order), condition = as.factor(condition), type = as.factor(type),  gender = as.factor(gender), age = as.numeric(age), education = as.numeric(education), NI = as.numeric(NI), TT = as.numeric(TT), HC = as.numeric(HC),intensity = as.numeric(intensity), acc = as.numeric(acc), rt = as.numeric(rt))
cen.stroop$condition  <- relevel(cen.stroop$condition, ref = "V")
cen.stroop.con        <- filter (cen.stroop, type == "con")
cen.stroop.incon      <- filter (cen.stroop, type == "incon")

cen.nback <- read_excel ("/Users/echo/Library/CloudStorage/OneDrive-UNSW/Brain_Stimulation/CEN_Study_One/Data_Analysis/results/cog/20230814_cen_cog.xlsx", sheet = "2-back")
cen.nback$session <- factor (cen.nback$session, levels = c('S1', 'S2', 'S3'))
cen.nback$session <- as.numeric(cen.nback$session)
cen.nback <- cen.nback %>%
  mutate(participant = as.factor(participant), task_order = as.factor(task_order), order = as.factor(order), condition = as.factor(condition), gender = as.factor(gender), age = as.numeric(age), education = as.numeric(education), NI = as.numeric(NI), TT = as.numeric(TT), HC = as.numeric(HC), intensity = as.numeric(intensity), rt = as.numeric(rt), dprime = as.numeric(dprime))
cen.nback$condition   <- relevel(cen.nback$condition, ref = "V")

cen.stroop.eeg <- read_excel ("/Users/echo/Library/CloudStorage/OneDrive-UNSW/Brain_Stimulation/CEN_Study_One/Data_Analysis/results/eeg/230815_cen_eeg.xlsx", sheet = "stroop")
cen.stroop.eeg <- cen.stroop.eeg[order(cen.stroop.eeg$participant),]
cen.stroop.eeg <- cen.stroop.eeg %>%
  mutate(participant = as.factor(participant), condition = as.factor(condition), gender = as.factor(gender), session = as.numeric(session), order = as.factor(order), age = as.numeric(age), education = as.numeric(education), intensity = as.numeric(intensity), stroop_n2_Fz = as.numeric(stroop_n2_Fz), stroop_n4_Cz = as.numeric(stroop_n4_Cz))
cen.stroop.eeg$condition  <- relevel(cen.stroop.eeg$condition, ref = "V")
cen.stroop.eeg.con        <- filter (cen.stroop.eeg, type == "con")
cen.stroop.eeg.incon      <- filter (cen.stroop.eeg, type == "incon")

cen.nback.eeg <- read_excel ("/Users/echo/Library/CloudStorage/OneDrive-UNSW/Brain_Stimulation/CEN_Study_One/Data_Analysis/results/eeg/230815_cen_eeg.xlsx", sheet = "nback")
cen.nback.eeg <- cen.nback.eeg[order(cen.nback.eeg$participant),]
cen.nback.eeg <- cen.nback.eeg %>%
  mutate(participant = as.factor(participant), condition = as.factor(condition), gender = as.factor(gender), session = as.numeric(session), order = as.factor(order), age = as.numeric(age), education = as.numeric(education), intensity = as.numeric(intensity), nback_p3_id_Pz = as.numeric(nback_p3_id_Pz), nback_p3_id_P1 = as.numeric(nback_p3_id_P1), nback_p3_id_P3 = as.numeric(nback_p3_id_P3), nback_n2_id_Fz = as.numeric(nback_n2_id_Fz), nback_p3_id_Fz = as.numeric(nback_p3_id_Fz))
cen.nback.eeg$condition   <- relevel(cen.nback.eeg$condition, ref = "V")
```

Silhouette width for every observation: within cluster distance C(i) and closest neighbor distance N(i)

C(i): the average euclidean distance from the observation to every other observation within the same cluster. 
N(i): the closest neighbor distance for an observation is the average distance from that observation to the points of the closest neighboring cluster. The smallest average distance to our observation is used as the closest neighbor distance. 

Si = 1- C(i)/N(i) if C(i) < N(i);
Si = 0            if C(i) = N(i);
Si = N(i)/C(i)-1  if C(i) > N(i);

1: Well matched to the cluster
0: On border between two clusters
-1: Better fit in neighboring cluster

Cluster analyses using residuals

```{r 2back cluster analysis, echo = FALSE}
# Data manipulation and calculate condition difference based on residuals
nback_rt_session_only     <- lmer(formula = rt ~  1 + session + (1 |participant), data = cen.nback)
nback_dprime_session_only <- lmer(formula = dprime ~  1 + session + (1 |participant), data = cen.nback)

# Predict residuals
cen.nback.new          <- cen.nback
cen.nback.new$session  <- cen.nback$session[3]
cen.nback$rt.resid     <- resid(nback_rt_session_only, newdata = cen.nback.new, re.form = ~ (1 | participant))
cen.nback$dprime.resid <- resid(nback_dprime_session_only, newdata = cen.nback.new, re.form = ~ (1 | participant))

cen.nback.rt.wide                        <- dcast(cen.nback, participant ~ condition, value.var = c("rt.resid"))
cen.nback.rt.wide$diff_rt_dlpfc          <- cen.nback.rt.wide$D-cen.nback.rt.wide$V
cen.nback.rt.wide$diff_rt_cerebellum     <- cen.nback.rt.wide$C-cen.nback.rt.wide$V

cen.nback.dprime.wide                            <- dcast(cen.nback, participant ~ condition, value.var = c("dprime.resid"))
cen.nback.dprime.wide$diff_dprime_dlpfc          <- cen.nback.dprime.wide$D-cen.nback.dprime.wide$V
cen.nback.dprime.wide$diff_dprime_cerebellum     <- cen.nback.dprime.wide$C-cen.nback.dprime.wide$V

# plot predicted residuals
plot(cen.nback.rt.wide$diff_rt_cerebellum, cen.nback.rt.wide$diff_rt_dlpfc, pch = 19)
abline(v=0, col="blue", lty=2)
abline(h=15, col="blue", lty=2)

plot(cen.nback.dprime.wide$diff_dprime_cerebellum, cen.nback.dprime.wide$diff_dprime_dlpfc, pch = 19)
abline(v=0, col="blue", lty=2)
abline(h=0, col="blue", lty=2)

#plot residual difference between active conditions and sham
ggplot(cen.nback.rt.wide, aes(diff_rt_dlpfc, diff_rt_cerebellum, color = participant)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "2-back RT Residuals") 

ggplot(cen.nback.dprime.wide, aes(diff_dprime_dlpfc, diff_dprime_cerebellum, color = participant)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "2-back Dprime Residuals")

#cluster analysis_rt
#Select columns of interest
cen.nback.cluster.rt <- as_tibble(cen.nback.rt.wide)
cen.nback.cluster.rt <- cen.nback.rt.wide[, c("diff_rt_dlpfc", "diff_rt_cerebellum")]
# cen.nback.cluster.rt |> select(diff_rt_dlpfc, diff_rt_cerebellum) |> cor(use="pairwise.complete.obs") |> round(2)
cen.nback.cluster.dprime <- as_tibble(cen.nback.dprime.wide)
cen.nback.cluster.dprime <- cen.nback.dprime.wide[, c("diff_dprime_dlpfc", "diff_dprime_cerebellum")]
# cen.nback.cluster.dprime |> select(diff_dprime_dlpfc, diff_dprime_cerebellum) |> cor(use="pairwise.complete.obs") |> round(2)

#normalization data frame
cen.nback.cluster.rt[, c("diff_rt_dlpfc", "diff_rt_cerebellum")] = scale(cen.nback.cluster.rt[, c("diff_rt_dlpfc", "diff_rt_cerebellum")])
cen.nback.cluster.dprime[, c("diff_dprime_dlpfc", "diff_dprime_cerebellum")] = scale(cen.nback.cluster.dprime[, c("diff_dprime_dlpfc", "diff_dprime_cerebellum")])

# Decide how many clusters to look at
n_clusters <- 10

# Initialize total within sum of squares error: wss
wss_rt <- numeric(n_clusters)
wss_dprime <- numeric(n_clusters)
set.seed(123)

# Look over 1 to n possible clusters
for (i in 1:n_clusters) {
  # Fit the model
  km_nback_rt <- kmeans(cen.nback.cluster.rt, centers = i, nstart = 20)
  km_nback_dprime <- kmeans(cen.nback.cluster.dprime, centers = i, nstart = 20)
  # Save the within cluster sum of squares
  wss_rt[i] <- km_nback_rt$tot.withinss
  wss_dprime[i] <- km_nback_dprime$tot.withinss
}

# Produce scree plots (Elbow methods)
wss_rt_df <- tibble(clusters = 1:n_clusters, wss_rt = wss_rt)
scree_plot_rt <- ggplot(wss_rt_df, aes(x = clusters, y = wss_rt, group = 1)) +
    geom_point(size = 4)+
    geom_line() +
    scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
    xlab('Number of clusters') +
    geom_hline(
        yintercept = wss_rt,
        linetype = 'dashed',
        col = c(rep('#000000',4),'#FF0000', rep('#000000', 5))
    )
scree_plot_rt

# Silhouette analysis_RT
sil_width <- map_dbl(2:10, function(k){
  model <- pam(x=cen.nback.cluster.rt, k = k)
  model$silinfo$avg.width
})
sil_df <- data.frame(
  k=2:10,
  sil_width = sil_width
)
ggplot(sil_df, aes(x=k, y = sil_width))+
  geom_line()+
  scale_x_continuous(breaks = 2:10)

# Silhouette plots, plot(pam(x=cen.nback.cluster.rt, k=2))
plot(silhouette(pam(x=cen.nback.cluster.rt, k=2)))
plot(silhouette(pam(x=cen.nback.cluster.rt, k=3)))
plot(silhouette(pam(x=cen.nback.cluster.rt, k=4)))
plot(silhouette(pam(x=cen.nback.cluster.rt, k=5)))
plot(silhouette(pam(x=cen.nback.cluster.rt, k=6)))

# Produce scree plots (Elbow methods)
wss_dprime_df <- tibble(clusters = 1:n_clusters, wss_rt = wss_rt)
scree_plot_dprime <- ggplot(wss_dprime_df, aes(x = clusters, y = wss_dprime, group = 1)) +
    geom_point(size = 4)+
    geom_line() +
    scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
    xlab('Number of clusters') +
    geom_hline(
        yintercept = wss_dprime,
        linetype = 'dashed',
        col = c(rep('#000000',4),'#FF0000', rep('#000000', 5))
    )
scree_plot_dprime

# Silhouette analysis_dprime
sil_width <- map_dbl(2:10, function(k){
  model <- pam(x=cen.nback.cluster.dprime, k = k)
  model$silinfo$avg.width
})
sil_df <- data.frame(
  k=2:10,
  sil_width = sil_width
)
ggplot(sil_df, aes(x=k, y = sil_width)) +
  geom_line() +
  scale_x_continuous(breaks = 2:10)

# Silhouette plots, plot(pam(x=cen.nback.cluster.rt, k=2))
plot(silhouette(pam(x=cen.nback.cluster.dprime, k=2)))
plot(silhouette(pam(x=cen.nback.cluster.dprime, k=3)))
plot(silhouette(pam(x=cen.nback.cluster.dprime, k=4)))
plot(silhouette(pam(x=cen.nback.cluster.dprime, k=5)))
plot(silhouette(pam(x=cen.nback.cluster.dprime, k=6)))

# Select number of clusters
k <- 3
set.seed(123)
# Build model with k clusters: km.out
km_nback_rt <- kmeans(cen.nback.cluster.rt, centers = k, nstart = 20)
km_nback_dprime <- kmeans(cen.nback.cluster.dprime, centers = k, nstart = 20)
cen.nback.rt.wide$cluster_rt_id <- factor(km_nback_rt$cluster)
cen.nback.dprime.wide$cluster_dprime_id <- factor(km_nback_dprime$cluster)

# check the sample number and mean in each cluster
count(cen.nback.rt.wide, cluster_rt_id)
# cen.nback.rt.wide %>% group_by(cluster_rt_id) %>% summarise_all(list(mean))
count(cen.nback.dprime.wide, cluster_dprime_id)
# cen.nback.dprime.wide%>% group_by(cluster_dprime_id) %>% summarise_all(list(mean))

ggplot(cen.nback.rt.wide, aes(diff_rt_dlpfc, diff_rt_cerebellum, color = cluster_rt_id)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "2-back RT")

ggplot(cen.nback.dprime.wide, aes(diff_dprime_dlpfc, diff_dprime_cerebellum, color = cluster_dprime_id)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "2-back dprime")

cen.nback.wide.new            <- cen.nback.rt.wide  %>% slice(rep(1:n(), each = 3))
cen.nback.eeg$cluster_rt <- cen.nback.wide.new$cluster_rt_id
cen_nback_p3_cluster         <- lmer(formula = nback_p3_id_Pz ~  1 + cluster_rt + session + (1 |participant), data = cen.nback.eeg)
cen_nback_n2_cluster         <- lmer(formula = nback_n2_id_Fz ~  1 + cluster_rt + session + (1 |participant), data = cen.nback.eeg)
summary(cen_nback_p3_cluster)
summary(cen_nback_n2_cluster)

```

```{r Stroop cluster analysis, echo=FALSE}
# Data manipulation and calculate condition difference based on residuals
stroop_con_session_only     <- lmer(formula = rt ~  1 + session + (1 |participant), data = cen.stroop.con)
stroop_incon_session_only   <- lmer(formula = rt ~  1 + session + (1 |participant), data = cen.stroop.incon)

# Predict residuals
cen.stroop.con.new            <- cen.stroop.con
cen.stroop.con.new$session    <- cen.stroop.con.new$session[3]
cen.stroop.con$rt.resid       <- resid(stroop_con_session_only, newdata = cen.stroop.con.new, re.form = ~ (1 | participant))
cen.stroop.incon.new          <- cen.stroop.incon
cen.stroop.incon.new$session  <- cen.stroop.incon.new$session[3]
cen.stroop.incon$rt.resid     <- resid(stroop_incon_session_only, newdata = cen.stroop.incon.new, re.form = ~ (1 | participant))

cen.stroop.con.wide                        <- dcast(cen.stroop.con, participant ~ condition, value.var = c("rt.resid"))
cen.stroop.con.wide$diff_rt_dlpfc          <- cen.stroop.con.wide$D-cen.stroop.con.wide$V
cen.stroop.con.wide$diff_rt_cerebellum     <- cen.stroop.con.wide$C-cen.stroop.con.wide$V

cen.stroop.incon.wide                        <- dcast(cen.stroop.incon, participant ~ condition, value.var = c("rt.resid"))
cen.stroop.incon.wide$diff_rt_dlpfc          <- cen.stroop.incon.wide$D-cen.stroop.incon.wide$V
cen.stroop.incon.wide$diff_rt_cerebellum     <- cen.stroop.incon.wide$C-cen.stroop.incon.wide$V

# plot predicted residuals
plot(cen.stroop.con.wide$diff_rt_cerebellum, cen.stroop.con.wide$diff_rt_dlpfc, pch = 19)
abline(v=0, col="blue", lty=2)
abline(h=15, col="blue", lty=2)

plot(cen.stroop.incon.wide$diff_rt_cerebellum, cen.stroop.incon.wide$diff_rt_dlpfc, pch = 19)
abline(v=0, col="blue", lty=2)
abline(h=15, col="blue", lty=2)

#plot difference between active conditions and sham
ggplot(cen.stroop.con.wide, aes(diff_rt_dlpfc, diff_rt_cerebellum, color = participant)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "Stroop Con RT") +
    xlim(-100, 100) +
    ylim(-100, 100)

ggplot(cen.stroop.incon.wide, aes(diff_rt_dlpfc, diff_rt_cerebellum, color = participant)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "Stroop Incon RT") +
  xlim(-110, 110) +
  ylim(-110, 110)

#cluster analysis_stroop_rt
#Select columns of interest
cen.stroop.con.cluster.rt <- as_tibble(cen.stroop.con.wide)
cen.stroop.con.cluster.rt <- cen.stroop.con.wide[, c("diff_rt_dlpfc", "diff_rt_cerebellum")]
# cen.stroop.con.cluster.rt |> select(diff_rt_dlpfc, diff_rt_cerebellum) |> cor(use="pairwise.complete.obs") |> round(2)
cen.stroop.incon.cluster.rt <- as_tibble(cen.stroop.incon.wide)
cen.stroop.incon.cluster.rt <- cen.stroop.incon.wide[, c("diff_rt_dlpfc", "diff_rt_cerebellum")]
# cen.stroop.incon.cluster.rt |> select(diff_rt_dlpfc, diff_rt_cerebellum) |> cor(use="pairwise.complete.obs") |> round(2)

#normalization data frame
cen.stroop.con.cluster.rt[, c("diff_rt_dlpfc", "diff_rt_cerebellum")] = scale(cen.stroop.con.cluster.rt[, c("diff_rt_dlpfc", "diff_rt_cerebellum")])
cen.stroop.incon.cluster.rt[, c("diff_rt_dlpfc", "diff_rt_cerebellum")] = scale(cen.stroop.incon.cluster.rt[, c("diff_rt_dlpfc", "diff_rt_cerebellum")])

# Decide how many clusters to look at
n_clusters <- 10

# Initialize total within sum of squares error: wss
wss_con_rt <- numeric(n_clusters)
wss_incon_rt <- numeric(n_clusters)
set.seed(123)

# Look over 1 to n possible clusters
for (i in 1:n_clusters) {
  # Fit the model
  km_stroop_con_rt <- kmeans(cen.stroop.con.cluster.rt, centers = i, nstart = 20)
  km_stroop_incon_rt <- kmeans(cen.stroop.incon.cluster.rt, centers = i, nstart = 20)
  # Save the within cluster sum of squares
  wss_con_rt[i] <- km_stroop_con_rt$tot.withinss
  wss_incon_rt[i] <- km_stroop_incon_rt$tot.withinss
}

# Produce scree plots (Elbow methods)
wss_con_rt_df <- tibble(clusters = 1:n_clusters, wss_con_rt = wss_con_rt)
scree_plot_con_rt <- ggplot(wss_con_rt_df, aes(x = clusters, y = wss_con_rt, group = 1)) +
    geom_point(size = 4)+
    geom_line() +
    scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
    xlab('Number of clusters') +
    geom_hline(
        yintercept = wss_con_rt,
        linetype = 'dashed',
        col = c(rep('#000000',4),'#FF0000', rep('#000000', 5))
    )
scree_plot_con_rt

# Silhouette analysis_con_rt
sil_width <- map_dbl(2:10, function(k){
  model <- pam(x=cen.stroop.con.cluster.rt, k = k)
  model$silinfo$avg.width
})
sil_df <- data.frame(
  k=2:10,
  sil_width = sil_width
)
ggplot(sil_df, aes(x=k, y = sil_width)) +
  geom_line() +
  scale_x_continuous(breaks = 2:10)

# Silhouette plots
plot(silhouette(pam(x=cen.stroop.con.cluster.rt, k=2)))
plot(silhouette(pam(x=cen.stroop.con.cluster.rt, k=3)))
plot(silhouette(pam(x=cen.stroop.con.cluster.rt, k=4)))
plot(silhouette(pam(x=cen.stroop.con.cluster.rt, k=5)))
plot(silhouette(pam(x=cen.stroop.con.cluster.rt, k=6)))

# Produce scree plots (Elbow methods)_incon_rt
wss_incon_rt_df <- tibble(clusters = 1:n_clusters, wss_incon_rt = wss_incon_rt)
scree_plot_incon_rt <- ggplot(wss_incon_rt_df, aes(x = clusters, y = wss_incon_rt, group = 1)) +
    geom_point(size = 4)+
    geom_line() +
    scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
    xlab('Number of clusters') +
    geom_hline(
        yintercept = wss_con_rt,
        linetype = 'dashed',
        col = c(rep('#000000',4),'#FF0000', rep('#000000', 5))
    )
scree_plot_incon_rt

# Silhouette analysis_dprime
sil_width <- map_dbl(2:10, function(k){
  model <- pam(x=cen.stroop.incon.cluster.rt, k = k)
  model$silinfo$avg.width
})
sil_df <- data.frame(
  k=2:10,
  sil_width = sil_width
)
ggplot(sil_df, aes(x=k, y = sil_width)) +
  geom_line() +
  scale_x_continuous(breaks = 2:10)

# Silhouette plots
plot(silhouette(pam(x=cen.stroop.incon.cluster.rt, k=2)))
plot(silhouette(pam(x=cen.stroop.incon.cluster.rt, k=3)))
plot(silhouette(pam(x=cen.stroop.incon.cluster.rt, k=4)))
plot(silhouette(pam(x=cen.stroop.incon.cluster.rt, k=5)))
plot(silhouette(pam(x=cen.stroop.incon.cluster.rt, k=6)))

# Select number of clusters
k <- 2
set.seed(123)
# Build model with k clusters: km.out
km_stroop_con_rt <- kmeans(cen.stroop.con.cluster.rt, centers = k, nstart = 20)
km_stroop_incon_rt <- kmeans(cen.stroop.incon.cluster.rt, centers = k, nstart = 20)
cen.stroop.con.wide$cluster_rt_id <- factor(km_stroop_con_rt$cluster)
cen.stroop.incon.wide$cluster_rt_id <- factor(km_stroop_incon_rt$cluster)

ggplot(cen.stroop.con.wide, aes(diff_rt_dlpfc, diff_rt_cerebellum, color = cluster_rt_id)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "Stroop Con RT")

ggplot(cen.stroop.incon.wide, aes(diff_rt_dlpfc, diff_rt_cerebellum, color = cluster_rt_id)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "Stroop Incon RT")

count(cen.stroop.con.wide, cluster_rt_id)
count(cen.stroop.incon.wide, cluster_rt_id)

# Use cluster analyses based on reaction times to check the difference in ERPs
cen.stroop.con.wide.new         <- cen.stroop.con.wide  %>% slice(rep(1:n(), each = 3))
cen.stroop.eeg.con$cluster_rt   <- cen.stroop.con.wide.new$cluster_rt_id
stroop_con_n2_cluster           <- lmer(formula = stroop_n2_Fz ~  1 + cluster_rt + session + (1 |participant), data = cen.stroop.eeg.con)
stroop_con_n4_cluster           <- lmer(formula = stroop_n4_Cz ~  1 + cluster_rt + session + (1 |participant), data = cen.stroop.eeg.con)
summary(stroop_con_n2_cluster)
summary(stroop_con_n4_cluster)

cen.stroop.incon.wide.new       <- cen.stroop.incon.wide  %>% slice(rep(1:n(), each = 3))
cen.stroop.eeg.incon$cluster_rt <- cen.stroop.incon.wide.new$cluster_rt_id
stroop_incon_n2_cluster         <- lmer(formula = stroop_n2_Fz ~  1 + cluster_rt + session + (1 |participant), data = cen.stroop.eeg.incon)
stroop_incon_n4_cluster         <- lmer(formula = stroop_n4_Cz ~  1 + cluster_rt + session + (1 |participant), data = cen.stroop.eeg.incon)
summary(stroop_incon_n2_cluster)
summary(stroop_incon_n4_cluster)

```

```{r Stroop Cluster Analyses}
k <- 2
set.seed(123)
# Build model with k clusters: km.out
km_stroop_con_rt <- kmeans(cen.stroop.con.cluster.rt, centers = k, nstart = 20)
km_stroop_incon_rt <- kmeans(cen.stroop.incon.cluster.rt, centers = k, nstart = 20)
cen.stroop.con.cluster$cluster_rt_id <- factor(km_stroop_con_rt$cluster)
cen.stroop.incon.cluster$cluster_rt_id <- factor(km_stroop_incon_rt$cluster)

ggplot(cen.stroop.con.cluster, aes(diff_rt_dlpfc, diff_rt_cerebellum, color = cluster_rt_id)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "Stroop Con RT")

ggplot(cen.stroop.incon.cluster, aes(diff_rt_dlpfc, diff_rt_cerebellum, color = cluster_rt_id)) +
    geom_point(alpha = 0.9) +
    xlab("DLPFC-Sham") +
    ylab("Cerebellum-Sham") +
    labs(title = "Stroop Incon RT")

cen.stroop.incon.cluster2 <- filter(cen.stroop.incon.cluster, cluster_rt_id == 2)
summary(cen.stroop.incon.cluster2)

chisq.test(cen.stroop.incon.cluster2$gender)
chisq.test(cen.stroop.incon.cluster2$order)
t.test(age ~ cluster_rt_id, data=cen.stroop.incon.cluster2)
t.test(education ~ cluster_rt_id, data=cen.stroop.incon.cluster2)
t.test(NI ~ cluster_rt_id, data=cen.stroop.incon.cluster2)
t.test(TT ~ cluster_rt_id, data=cen.stroop.incon.cluster2)
t.test(HC ~ cluster_rt_id, data=cen.stroop.incon.cluster2)
t.test(intensity ~ cluster_rt_id, data=cen.stroop.incon.cluster2)

# EEG
cen.stroop.incon.cluster           <- cen.stroop.incon.cluster %>% slice(rep(1:n(), each = 3))
cen.stroop.eeg.incon$cluster_rt    <- cen.stroop.incon.cluster$cluster_rt_id
cen.stroop.eeg.incon.cluster2      <- filter(cen.stroop.eeg.incon, cluster_rt == 2)
cen_nback_p3_cluster               <- lmer(formula = nback_p3_id_Pz ~  1 + cluster_rt + session + (1 |participant), data = cen.stroop.eeg.incon.cluster2)

```


```{r check correlations of ie, erps in stroop}
cen.stroop.con$ie        <- cen.stroop.con$rt-cen.stroop.incon$rt
stroop_ie_session_only   <- lmer(formula = ie ~  1 + session + (1 |participant), data = cen.stroop.con)

cen.stroop.ie            <- cen.stroop.con
cen.stroop.ie$session    <- cen.stroop.con$session[3]
cen.stroop.ie$rt.resid   <- resid(stroop_ie_session_only, newdata = cen.stroop.ie, re.form = ~ (1 | participant))

cen.stroop.ie.wide                        <- dcast(cen.stroop.ie, participant ~ condition, value.var = c("rt.resid"))
cen.stroop.ie.wide$diff_rt_dlpfc          <- cen.stroop.ie.wide$D-cen.stroop.ie.wide$V
cen.stroop.ie.wide$diff_rt_cerebellum     <- cen.stroop.ie.wide$C-cen.stroop.ie.wide$V
cor.test(cen.stroop.ie.wide$diff_rt_dlpfc, cen.stroop.ie.wide$diff_rt_cerebellum)
cor.test(cen.stroop.con.wide$diff_rt_dlpfc, cen.stroop.con.wide$diff_rt_cerebellum)
cor.test(cen.stroop.incon.wide$diff_rt_dlpfc, cen.stroop.incon.wide$diff_rt_cerebellum)

# EEG outcomes
# Stroop congruent
stroop_con_n2_session_only   <- lmer(formula = stroop_n2_Fz ~  1 + session + (1 |participant), data = cen.stroop.eeg.con)
stroop_con_n4_session_only   <- lmer(formula = stroop_n4_Cz ~  1 + session + (1 |participant), data = cen.stroop.eeg.con)

cen.stroop.con.n2            <- cen.stroop.con
cen.stroop.con.n2$session    <- cen.stroop.con$session[3]
cen.stroop.con.n2$n2.resid   <- resid(stroop_con_n2_session_only, newdata = cen.stroop.con.n2, re.form = ~ (1 | participant))
cen.stroop.con.n2.wide                        <- dcast(cen.stroop.con.n2, participant ~ condition, value.var = c("n2.resid"))
cen.stroop.con.n2.wide$diff_rt_dlpfc          <- cen.stroop.con.n2.wide$D-cen.stroop.con.n2.wide$V
cen.stroop.con.n2.wide$diff_rt_cerebellum     <- cen.stroop.con.n2.wide$C-cen.stroop.con.n2.wide$V
cor.test(cen.stroop.con.n2.wide$diff_rt_dlpfc, cen.stroop.con.n2.wide$diff_rt_cerebellum)

cen.stroop.con.n4            <- cen.stroop.con
cen.stroop.con.n4$session    <- cen.stroop.con$session[3]
cen.stroop.con.n4$n4.resid   <- resid(stroop_con_n4_session_only, newdata = cen.stroop.con.n4, re.form = ~ (1 | participant))
cen.stroop.con.n4.wide                        <- dcast(cen.stroop.con.n4, participant ~ condition, value.var = c("n4.resid"))
cen.stroop.con.n4.wide$diff_rt_dlpfc          <- cen.stroop.con.n4.wide$D-cen.stroop.con.n4.wide$V
cen.stroop.con.n4.wide$diff_rt_cerebellum     <- cen.stroop.con.n4.wide$C-cen.stroop.con.n4.wide$V
cor.test(cen.stroop.con.n4.wide$diff_rt_dlpfc, cen.stroop.con.n4.wide$diff_rt_cerebellum)

# Stroop incongruent
stroop_incon_n2_session_only   <- lmer(formula = stroop_n2_Fz ~  1 + session + (1 |participant), data = cen.stroop.eeg.incon)
stroop_incon_n4_session_only   <- lmer(formula = stroop_n4_Cz ~  1 + session + (1 |participant), data = cen.stroop.eeg.incon)

cen.stroop.incon.n2            <- cen.stroop.incon
cen.stroop.incon.n2$session    <- cen.stroop.incon$session[3]
cen.stroop.incon.n2$n2.resid   <- resid(stroop_incon_n2_session_only, newdata = cen.stroop.incon.n2, re.form = ~ (1 | participant))
cen.stroop.incon.n2.wide                        <- dcast(cen.stroop.incon.n2, participant ~ condition, value.var = c("n2.resid"))
cen.stroop.incon.n2.wide$diff_rt_dlpfc          <- cen.stroop.incon.n2.wide$D-cen.stroop.incon.n2.wide$V
cen.stroop.incon.n2.wide$diff_rt_cerebellum     <- cen.stroop.incon.n2.wide$C-cen.stroop.incon.n2.wide$V
cor.test(cen.stroop.incon.n2.wide$diff_rt_dlpfc, cen.stroop.incon.n2.wide$diff_rt_cerebellum)

cen.stroop.incon.n4            <- cen.stroop.incon
cen.stroop.incon.n4$session    <- cen.stroop.incon$session[3]
cen.stroop.incon.n4$n4.resid   <- resid(stroop_incon_n4_session_only, newdata = cen.stroop.incon.n4, re.form = ~ (1 | participant))
cen.stroop.incon.n4.wide                        <- dcast(cen.stroop.incon.n4, participant ~ condition, value.var = c("n4.resid"))
cen.stroop.incon.n4.wide$diff_rt_dlpfc          <- cen.stroop.incon.n4.wide$D-cen.stroop.incon.n4.wide$V
cen.stroop.incon.n4.wide$diff_rt_cerebellum     <- cen.stroop.incon.n4.wide$C-cen.stroop.incon.n4.wide$V
cor.test(cen.stroop.incon.n4.wide$diff_rt_dlpfc, cen.stroop.incon.n4.wide$diff_rt_cerebellum)

#2-back
nback_p3_session_only   <- lmer(formula = nback_p3_id_Pz ~  1 + session + (1 |participant), data = cen.nback.eeg)
nback_n2_session_only   <- lmer(formula = nback_n2_id_Fz ~  1 + session + (1 |participant), data = cen.nback.eeg)

cen.nback.eeg.n2            <- cen.nback.eeg
cen.nback.eeg.n2$session    <- cen.nback.eeg$session[3]
cen.nback.eeg.n2$n2.resid   <- resid(nback_n2_session_only, newdata = cen.nback.eeg.n2, re.form = ~ (1 | participant))
cen.nback.eeg.n2.wide                        <- dcast(cen.nback.eeg.n2, participant ~ condition, value.var = c("n2.resid"))
cen.nback.eeg.n2.wide$diff_rt_dlpfc          <- cen.nback.eeg.n2.wide$D-cen.nback.eeg.n2.wide$V
cen.nback.eeg.n2.wide$diff_rt_cerebellum     <- cen.nback.eeg.n2.wide$C-cen.nback.eeg.n2.wide$V
cor.test(cen.nback.eeg.n2.wide$diff_rt_dlpfc, cen.nback.eeg.n2.wide$diff_rt_cerebellum)

cen.nback.eeg.p3            <- cen.nback.eeg
cen.nback.eeg.p3$session    <- cen.nback.eeg$session[3]
cen.nback.eeg.p3$p3.resid   <- resid(nback_p3_session_only, newdata = cen.nback.eeg.p3, re.form = ~ (1 | participant))
cen.nback.eeg.p3.wide                        <- dcast(cen.nback.eeg.p3, participant ~ condition, value.var = c("p3.resid"))
cen.nback.eeg.p3.wide$diff_rt_dlpfc          <- cen.nback.eeg.p3.wide$D-cen.nback.eeg.p3.wide$V
cen.nback.eeg.p3.wide$diff_rt_cerebellum     <- cen.nback.eeg.p3.wide$C-cen.nback.eeg.p3.wide$V
cor.test(cen.nback.eeg.p3.wide$diff_rt_dlpfc, cen.nback.eeg.p3.wide$diff_rt_cerebellum)

```

